### 2023-07-31 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed small typo

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
%  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
%  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(black) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}
